Manuscript

### 2017-07-14 manuscript.Rmd
Simplify and remove redundant code
I've used the lapply family of functions to loop over our dependent variables and our cities, so that we don't have to run every function 3 * 3 times.

```{r setup}
library(geojsonio)
library(leaflet)
library(tidyverse)
library(spdep)
library(maptools)
library(rgdal)
library(rgeos)
library(texreg)
library(leaflet)
```

@@

# Methods
```{r load_data}
denver_tracts <- geojson_read("data/denver_tracts.geojson", what = "sp")
denver_parks <- geojson_read ("data/denver_parks.geojson", what = "sp")

@@

nyc_tracts <- geojson_read("data/nyc_tracts.geojson", what = "sp")
nyc_parks <- geojson_read("data/nyc_parks.geojson", what = "sp")
```

@@

Transform the attribute table into a tibble and select the relevant variables:
```{r show_denverdata}
denver_tracts@data <- tbl_df(tracts@data) %>%
  select(GEOID_TRAC, OBESITY, Park_Percent, PhysAct, MENTAL, Income1, Income2, Income3, Income4, Income5, Income6, Income7, Income8, Income9, Income10, Pop_Density, FulltimeWork, CollegePercent, Pct0to17, Pct18to29, Pct30to64, Pct65plus, SinglePercent, PctWhite, PctBlack, PctNative, PctAsian, PctPacific, PctOther, PctHispanic) %>%
    mutate_each(funs(ifelse(is.na(.), 0, .)), Park_Percent)
tracts@data
```

Calculate the logsum given the tracts and parks dataset:
```{r denver_accessibility}
source('R/denver_size00001dist5.R', echo=TRUE)
denver_tracts$park_ls <- calculate_park_logsums(denver_tracts, denver_parks, betas = c(.00001, -5))
```

Create regression equations for use in spatial econometric models:
```{r denver_equations}
denver_base_formula <- formula(~Income1 + Income2 + Income3 + Income4 + Income5 + Income6 + Income7 + Income8 + Income9 + Income10 + log(Pop_Density) + FulltimeWork + CollegePercent + SinglePercent + Pct0to17 + Pct18to29 + Pct30to64 + Pct65plus + PctWhite + PctBlack + PctNative + PctAsian + PctPacific + PctOther + PctHispanic)

denver_parks_formula <- update(base_formula, . ~ . + park_ls)
```

Locate the centroid of all parks and all census tracts and create a distance matrix:
```{r denver_distancematrix}
denver_tract_centroids <- gCentroid(denver_tracts, byid = TRUE) #if byid = FALSE, then centroid of "all" points
denver_park_centroids <- gCentroid(denver_parks, byid = TRUE)
distance_matrix <- gDistance(denver_tract_centroids, denver_park_centroids, byid = TRUE)
dim(denver_distance_matrix)
```

Create a spatial weights matrix:
```{r denver_W}
denver_neighbors <- poly2nb(denver_tracts, queen = FALSE)
denver_W <- nb2listw(neighbours = denver_neighbors, zero.policy = TRUE)
print(denver_W, zero.policy = TRUE)
```

Estimate spatial econometric models for the `OBESITY` variable. The first model of each different type does not include `park_ls`:
```{r denver_spmodels_obesity}
denver_obese_sem <- errorsarlm(update(denver_base_formula, OBESITY ~ .), data = denver_tracts@data, 
                      listw = denver_W, zero.policy = TRUE)
denver_obese_sem2 <- errorsarlm(update(denver_parks_formula, OBESITY ~ .), data = denver_tracts@data, 
                      listw = denver_W, zero.policy = TRUE)
denver_obese_sdm <- lagsarlm(update(denver_base_formula, OBESITY ~ .), data = denver_tracts@data, 
                      listw = denver_W, zero.policy = TRUE, type = "mixed")
denver_obese_sdm2 <- lagsarlm(update(denver_parks_formula, OBESITY ~ .), data = denver_tracts@data, 
                      listw = denver_W, zero.policy = TRUE, type = "mixed")
```

Estimate spatial econometric models for the `PhysAct` variable. The first model of each different type does not include `park_ls`:
```{r denver_spmodels_physact}
denver_physact_sem <- errorsarlm(update(denver_base_formula, PhysAct ~ .), data = denver_tracts@data, 
                          listw = denver_W, zero.policy = TRUE)
denver_physact_sem2 <- errorsarlm(update(denver_parks_formula, PhysAct ~ .), 
                           data = denver_tracts@data, listw = denver_W, zero.policy = TRUE)
denver_physact_sdm <- lagsarlm(update(denver_base_formula, PhysAct ~ .), data = denver_tracts@data, 
                        listw = denver_W, zero.policy = TRUE, type = "mixed")
denver_physact_sdm2 <- lagsarlm(update(denver_parks_formula, PhysAct ~ .), data = denver_tracts@data,
                         listw = denver_W, zero.policy = TRUE, type = "mixed")
```

Estimate spatial econometric models for the `MENTAL` variable. The first model of each different type does not include `park_ls`:
```{r denver_spmodels_mental}
denver_mental_sem <- errorsarlm(update(denver_base_formula, MENTAL ~ .), data = denver_tracts@data, 
                          listw = denver_W, zero.policy = TRUE)
denver_mental_sem2 <- errorsarlm(update(denver_parks_formula, MENTAL ~ .), 
                           data = denver_tracts@data, listw = denver_W, zero.policy = TRUE)
denver_mental_sdm <- lagsarlm(update(denver_base_formula, MENTAL ~ .), data = denver_tracts@data, 
                        listw = denver_W, zero.policy = TRUE, type = "mixed")
denver_mental_sdm2 <- lagsarlm(update(denver_parks_formula, MENTAL ~ .), data = denver_tracts@data,
                         listw = denver_W, zero.policy = TRUE, type = "mixed")
```

Calculate the impacts of the spatial durbin models:
```{r denverSDM_impacts}
denver_listw <- as(denver_W, "CsparseMatrix")
denver_tr_mult <- trW(denver_listw, type="mult")
denver_tr_MC <- trW(denver_listw, type="MC")
set.seed(1)

denver_noparks_obesemult <- impacts(denver_obese_sdm, tr=denver_tr_mult)
denver_parks_obesemult <- impacts(denver_obese_sdm2, tr=denver_tr_mult)
denver_noparks_obeseMC <- impacts(denver_obese_sdm, tr=denver_tr_MC)
denver_parks_obeseMC <- impacts(denver_obese_sdm2, tr=denver_tr_MC)

denver_noparks_physactmult <- impacts(denver_physact_sdm, tr=denver_tr_mult)
denver_parks_physactmult <- impacts(denver_physact_sdm2, tr=denver_tr_mult)
denver_noparks_physactMC <- impacts(denver_physact_sdm, tr=denver_tr_MC)
denver_parks_physactMC <- impacts(denver_physact_sdm2, tr=denver_tr_MC)

denver_noparks_mentalmult <- impacts(denver_mental_sdm, tr=denver_tr_mult)
denver_parks_mentalmult <- impacts(denver_mental_sdm2, tr=denver_tr_mult)
denver_noparks_mentalMC <- impacts(denver_mental_sdm, tr=denver_tr_MC)
denver_parks_mentalMC <- impacts(denver_mental_sdm2, tr=denver_tr_MC)
```

Compare the models with `htmlreg()`. First the obesity models:
```{r denver_obesity_summary, results="asis", eval=FALSE}
denver_obesity_models <- list(denver_obese_sem, denver_obese_sem2, denver_obese_sdm, denver_obese_sdm2)
names(denver_obesity_models) <-  paste(rep(c("SEM", "SDM"), each = 2),
                                rep(c("Base", "Parks")))
htmlreg(denver_obesity_models, caption = "Denver: Models of Obesity Prevalence")
```

Next, the physical activity models:
```{r denver_physact_summary, results="asis", eval=FALSE}
denver_physact_models <- list(denver_physact_sem, denver_physact_sem2, denver_physact_sdm, denver_physact_sdm2)
names(denver_physact_models) <-  paste(rep(c("SEM", "SDM"), each = 2),
                                rep(c("Base", "Parks")))
htmlreg(denver_physact_models, caption = "Denver: Models of Physical Activity Participation")
```

And third, the mental health models:
```{r denver_mental_summary, results="asis", eval=FALSE}
denver_mental_models <- list(denver_mental_sem, denver_mental_sem2, denver_mental_sdm, denver_mental_sdm2)
names(denver_mental_models) <-  paste(rep(c("SEM", "SDM"), each = 2),
                                rep(c("Base", "Parks")))
htmlreg(denver_physact_models, caption = "Denver: Models of Variation in Self-Reported Mental Health")
```

## Boston

Plot Boston geospatial data (tracts and parks):
```{r boston_data}
#boston_tracts2 <- readOGR(dsn = "data/Boston_Data.gdb", layer = "Boston_Final")
plot(boston_tracts)

#boston_parks2 <- readOGR(dsn = "data/Boston_Data.gdb", layer = "Boston_All_Parks") 
plot(boston_parks)
```

Transform the attribute table into a tibble and select the relevant variables:
```{r show_bostondata}
tracts@data <- tbl_df(tracts@data) %>%
  select(GEOID10, OBESITY, Phys_Act, MENTAL, Park_Percent, Income1, Income2, Income3, Income4, Income5, Income6, Income7, Income8, Income9, Income10, Pop_Density, FulltimeWork, CollegeDeg, Pct0to17, Pct18to29, Pct30to64, Pct65plus, SinglePercent, PctWhite, PctBlack, PctNative, PctAsian, PctPacific, PctOther, PctHispanic)
tracts@data
```

Calculate the logsum given the tracts and parks dataset:
```{r boston_accessibility}
source('boston_size00001dist30.R', echo=TRUE)
boston_tracts$park_ls <- calculate_park_logsums(boston_tracts, boston_parks, betas = c(.00001, -30))
```

Create regression equations for use in spatial econometric models:
```{r boston_equations}
boston_base_formula <- formula(~Income1 + Income2 + Income3 + Income4 + Income5 + Income6 + Income7 + Income8 + Income9 + Income10 + log(Pop_Density) + FulltimeWork + CollegeDeg + SinglePercent + Pct0to17 + Pct18to29 + Pct30to64 + Pct65plus + PctWhite + PctBlack + PctNative + PctAsian + PctPacific + PctOther + PctHispanic)

boston_parks_formula <- update(base_formula, . ~ . + park_ls)
```

Locate the centroid of all parks and all census tracts and create a distance matrix:
```{r boston_distancematrix}
boston_tract_centroids <- gCentroid(boston_tracts, byid = TRUE) #if byid = FALSE, then centroid of "all" points
boston_park_centroids <- gCentroid(boston_parks, byid = TRUE)
boston_distance_matrix <- gDistance(boston_tract_centroids, boston_park_centroids, byid = TRUE)
dim(boston_distance_matrix)
```

Create a spatial weights matrix:
```{r boston_W}
boston_neighbors <- poly2nb(boston_tracts, queen = FALSE)
boston_W <- nb2listw(neighbours = boston_neighbors, zero.policy = TRUE)
print(boston_W, zero.policy = TRUE)
```

Estimate spatial econometric models for the `OBESITY` variable. The first model of each different type does not include `park_ls`:
```{r boston_spmodels_obesity}
boston_obese_sem <- errorsarlm(update(boston_base_formula, OBESITY ~ .), data = boston_tracts@data, 
                      listw = boston_W, zero.policy = TRUE)
boston_obese_sem2 <- errorsarlm(update(boston_parks_formula, OBESITY ~ .), data = boston_tracts@data, 
                      listw = boston_W, zero.policy = TRUE)
boston_obese_sdm <- lagsarlm(update(boston_base_formula, OBESITY ~ .), data = boston_tracts@data, 
                      listw = boston_W, zero.policy = TRUE, type = "mixed")
boston_obese_sdm2 <- lagsarlm(update(boston_parks_formula, OBESITY ~ .), data = boston_tracts@data, 
                      listw = boston_W, zero.policy = TRUE, type = "mixed")
```

Estimate spatial econometric models for the `PhysAct` variable. The first model of each different type does not include `park_ls`:
```{r boston_spmodels_physact}
boston_physact_sem <- errorsarlm(update(boston_base_formula, Phys_Act ~ .), data = boston_tracts@data, 
                          listw = boston_W, zero.policy = TRUE)
boston_physact_sem2 <- errorsarlm(update(boston_parks_formula, Phys_Act ~ .), 
                           data = boston_tracts@data, listw = boston_W, zero.policy = TRUE)
boston_physact_sdm <- lagsarlm(update(boston_base_formula, Phys_Act ~ .), data = boston_tracts@data, 
                        listw = boston_W, zero.policy = TRUE, type = "mixed")
boston_physact_sdm2 <- lagsarlm(update(boston_parks_formula, Phys_Act ~ .), data = boston_tracts@data,
                         listw = boston_W, zero.policy = TRUE, type = "mixed")
```

Estimate spatial econometric models for the `MENTAL` variable. The first model of each different type does not include `park_ls`:
```{r boston_spmodels_mental}
boston_mental_sem <- errorsarlm(update(boston_base_formula, MENTAL ~ .), data = boston_tracts@data, 
                          listw = boston_W, zero.policy = TRUE)
boston_mental_sem2 <- errorsarlm(update(boston_parks_formula, MENTAL ~ .), 
                           data = boston_tracts@data, listw = boston_W, zero.policy = TRUE)
boston_mental_sdm <- lagsarlm(update(boston_base_formula, MENTAL ~ .), data = boston_tracts@data, 
                        listw = boston_W, zero.policy = TRUE, type = "mixed")
boston_mental_sdm2 <- lagsarlm(update(boston_parks_formula, MENTAL ~ .), data = boston_tracts@data,
                         listw = boston_W, zero.policy = TRUE, type = "mixed")
```

Calculate the impacts of the spatial durbin models:
```{r bostonSDM_impacts}
boston_listw <- as(boston_W, "CsparseMatrix")
boston_tr_mult <- trW(boston_listw, type="mult")
boston_tr_MC <- trW(boston_listw, type="MC")
set.seed(1)

boston_noparks_obesemult <- impacts(boston_obese_sdm, tr=boston_tr_mult)
boston_parks_obesemult <- impacts(boston_obese_sdm2, tr=boston_tr_mult)
boston_noparks_obeseMC <- impacts(boston_obese_sdm, tr=boston_tr_MC)
boston_parks_obeseMC <- impacts(boston_obese_sdm2, tr=boston_tr_MC)

boston_noparks_physactmult <- impacts(boston_physact_sdm, tr=boston_tr_mult)
boston_parks_physactmult <- impacts(boston_physact_sdm2, tr=boston_tr_mult)
boston_noparks_physactMC <- impacts(boston_physact_sdm, tr=boston_tr_MC)
boston_parks_physactMC <- impacts(boston_physact_sdm2, tr=boston_tr_MC)

boston_noparks_mentalmult <- impacts(boston_mental_sdm, tr=boston_tr_mult)
boston_parks_mentalmult <- impacts(boston_mental_sdm2, tr=boston_tr_mult)
boston_noparks_mentalMC <- impacts(boston_mental_sdm, tr=boston_tr_MC)
boston_parks_mentalMC <- impacts(boston_mental_sdm2, tr=boston_tr_MC)
```

Compare the models with `htmlreg()`. First the obesity models:
```{r boston_obesity_summary, results="asis", eval=FALSE}
boston_obesity_models <- list(boston_obese_sem, boston_obese_sem2, boston_obese_sdm, boston_obese_sdm2)
names(boston_obesity_models) <-  paste(rep(c("SEM", "SDM"), each = 2),
                                rep(c("Base", "Parks")))
htmlreg(boston_obesity_models, caption = "Boston: Models of Obesity Prevalence")
```

Next, the physical activity models:
```{r boston_physact_summary, results="asis", eval=FALSE}
boston_physact_models <- list(boston_physact_sem, boston_physact_sem2, boston_physact_sdm, boston_physact_sdm2)
names(boston_physact_models) <-  paste(rep(c("SEM", "SDM"), each = 2),
                                rep(c("Base", "Parks")))
htmlreg(boston_physact_models, caption = "Boston: Models of Physical Activity Participation")
```

And third, the mental health models:
```{r boston_mental_summary, results="asis", eval=FALSE}
boston_mental_models <- list(boston_mental_sem, boston_mental_sem2, boston_mental_sdm, boston_mental_sdm2)
names(boston_mental_models) <-  paste(rep(c("SEM", "SDM"), each = 2),
                                rep(c("Base", "Parks")))
htmlreg(boston_physact_models, caption = "Boston: Models of Variation in Self-Reported Mental Health")
```

##New York City
```{r nyc_models}

```

>>>>

```{r setup}
library(geojsonio)
library(leaflet)
library(tidyverse)
library(spdep)
library(maptools)
library(rgdal)
library(rgeos)
library(texreg)
library(leaflet)

# source functions
source("R/logsums.R")

# variables
cities <- c("denver", "boston", "nyc")
```

@@

# Methods
```{r load_data}
denver_tracts <- geojson_read("data/denver_tracts.geojson", what = "sp")
denver_tracts$GEOID10 <- denver_tracts$GEOID_TRAC
denver_parks <- geojson_read ("data/denver_parks.geojson", what = "sp")

@@

nyc_tracts <- geojson_read("data/nyc_tracts.geojson", what = "sp")
nyc_parks <- geojson_read("data/nyc_parks.geojson", what = "sp")

tract_shapes <- list(denver_tracts, boston_tracts, nyc_tracts)
park_shapes <- list(denver_parks, boston_parks, nyc_parks)
```

@@

Transform the attribute table into a tibble and select the relevant variables:
```{r transformdata}
#TODO: make sure all cities have the same data in the same names. It will save 
# us LOTS of time
# denver only, because the other cities have different variables
regression_data <-
  lapply(seq_along(1:1), function(i) {
    tbl_df(tract_shapes[[i]]@data) %>%
      mutate(
        Park_Percent = ifelse(is.na(Park_Percent), 0, Park_Percent),
        city = cities[i]
      )
  })
```

DISCUSSION OF LOGSUM CALCULATION

Calculate the logsum given the tracts and parks dataset:
```{r accessibility}
regression_data[[1]]["park_ls"] <- calculate_park_logsums(
  denver_tracts, denver_parks, betas = c(.00001, -5))
regression_data[[2]]["park_ls"] <- calculate_park_logsums(
  boston_tracts, boston_parks, betas = c(.00001, -30))
regression_data[[1]]["park_ls"] <- calculate_park_logsums(
  nyc_tracts, nyc_parks, betas = c(.00001, -5))
```

Create regression equations for use in spatial econometric models:
```{r regression_eq}
base_formula <- formula(
  ~ Income1 + Income2 + Income3 + Income4 + Income5 + Income6 + Income7 + 
    Income8 + Income9 + Income10 + log(Pop_Density) + FulltimeWork + 
    CollegePercent + SinglePercent + Pct0to17 + Pct18to29 + Pct30to64 + 
    Pct65plus + PctWhite + PctBlack + PctNative + PctAsian + PctPacific + 
    PctOther + PctHispanic)

parks_formula <- update(base_formula, . ~ . + park_ls)
```

Locate the centroid of all parks and all census tracts and create a distance matrix:
```{r distancematrix}
# why are we computing the distance matrices if we are using contiguity-based
# neighbors?
tract_centroids <- lapply(seq_along(1:length(cities)), function(i){
  gCentroid(tract_shapes[[i]], byid = TRUE)
})

park_centroids <- lapply(seq_along(1:length(cities)), function(i){
  gCentroid(park_shapes[[i]], byid = TRUE)
})

distance_matrices <- lapply(seq_along(1:length(cities)), function(i){
  gDistance(tract_centroids[[i]], park_centroids[[i]], byid = TRUE)
})

names(distance_matrices) <- names(tract_centroids) <- names(park_centroids) <- cities
```

```{r listw}
list_ws <- lapply(seq_along(1:length(cities)), function(i){
  nb <- poly2nb(tract_shapes[[i]], queen = FALSE)
  nb2listw(neighbours = nb, zero.policy = TRUE)
})
names(list_ws) <- cities
```

Estimate spatial econometric models for the `OBESITY` variable. The first model
of each different type does not include `park_ls`:

```{r linear_models}
# this lets us run all of the linear models (for all the cities) in like ten 
# lines of code
dependent_variables <- c("OBESITY", "PhysAct", "MENTAL")

base_lm <- lapply(seq_along(1:length(dependent_variables)), function(i){

  this_formula <- substitute(update(base_formula, x ~ .), 
                             list(x = as.name(dependent_variables[i]) ))

  bind_rows(regression_data) %>%
    split(.$city) %>%
    map(~lm(this_formula, data = .))
})

parks_lm <- lapply(seq_along(1:length(dependent_variables)), function(i){

  this_formula <- substitute(update(parks_formula, x ~ .), 
                             list(x = as.name(dependent_variables[i]) ))

  bind_rows(regression_data) %>%
    split(.$city) %>%
    map(~lm(this_formula, data = .))
})

names(parks_lm) <- names(base_lm) <- dependent_variables
# get a model with summary(base_lm$OBESITY$denver), for instance.
```

```{r sem}
base_sem <- lapply(seq_along(1:length(dependent_variables)), function(dv){
  this_formula <- substitute(update(base_formula, x ~ .), 
                             list(x = as.name(dependent_variables[dv]) ))

  # TODO update when more cities are available
  models <- lapply(seq_along(1:1), function(city){
    errorsarlm(this_formula, data = regression_data[[city]],
               listw = list_ws[[city]], zero.policy = TRUE)
  })

  names(models) <- cities[1]
  return(models)
})

park_sem <- lapply(seq_along(1:length(dependent_variables)), function(dv){
  this_formula <- substitute(update(parks_formula, x ~ .), 
                             list(x = as.name(dependent_variables[dv]) ))

  # TODO update when more cities are available
  models <- lapply(seq_along(1:1), function(city){
    errorsarlm(this_formula, data = regression_data[[city]],
               listw = list_ws[[city]], zero.policy = TRUE)
  })

  names(models) <- cities[1]
  return(models)
})

names(park_sem) <- names(base_sem) <- dependent_variables
```

```{r sdm}
base_sdm <- lapply(seq_along(1:length(dependent_variables)), function(dv){
  this_formula <- substitute(update(base_formula, x ~ .), 
                             list(x = as.name(dependent_variables[dv]) ))

  # TODO update when more cities are available
  models <- lapply(seq_along(1:1), function(city){
    lagsarlm(this_formula, data = regression_data[[city]],
             listw = list_ws[[city]], zero.policy = TRUE, type = "mixed")
  })

  names(models) <- cities[1]
  return(models)
})

park_sdm <- lapply(seq_along(1:length(dependent_variables)), function(dv){
  this_formula <- substitute(update(parks_formula, x ~ .), 
                             list(x = as.name(dependent_variables[dv]) ))

  # TODO update when more cities are available
  models <- lapply(seq_along(1:1), function(city){
    lagsarlm(this_formula, data = regression_data[[city]],
             listw = list_ws[[city]], zero.policy = TRUE, type = "mixed")
  })

  names(models) <- cities[1]
  return(models)
})

names(park_sdm) <- names(base_sdm) <- dependent_variables
```

Calculate the impacts of the spatial durbin models:
```{r SDM_impacts}
tr_mc <- lapply(list_ws, function(x){
  trW(as(x, "CsparseMatrix"), type="MC")
})

mc_impacts <- lapply(base_sdm, function(dv){
  # TODO
  impacts <- lapply(seq_along(1:1), function(i) {
    impacts(dv[[i]], tr = tr_mc[[i]])
  })

  names(impacts) <- cities[i]

  return(impacts)
})
names(mc_impacts) <- dependent_variables
```

Compare the models with `htmlreg()`. First the obesity models:
```{r denver_obesity_summary, results="asis", eval=FALSE}
denver_obesity_models <- list(
  base_sem$OBESITY$denver, park_sem$OBESITY$denver,
  base_sdm$OBESITY$denver, park_sdm$OBESITY$denver
)

names(denver_obesity_models) <- paste(rep(c("SEM", "SDM"), each = 2), 
                                      rep(c("Base", "Parks")))

htmlreg(denver_obesity_models, caption = "Denver: Models of Obesity Prevalence")
```

Next, the physical activity models:
```{r denver_physact_summary, results="asis", eval=FALSE}
denver_physact_models <- list(
  base_sem$PhysAct$denver, park_sem$PhysAct$denver,
  base_sdm$PhysAct$denver, park_sdm$PhysAct$denver
)
names(denver_physact_models) <- paste(rep(c("SEM", "SDM"), each = 2),
                                      rep(c("Base", "Parks")))
htmlreg(denver_physact_models, caption = "Denver: Models of Physical Activity Participation")
```

And third, the mental health models:
